\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
\renewcommand{\thesection}{\Alph{section}}

\section{SUS Questions}\label{SUS}
Below is the list of the 10 specific questions with each containing the answers ranging from Strongly Disagree to Strongly Agree. 

\begin{enumerate}
    \item I think i would like to use this system more frequently.
    \item I found the system unnecessarily complex.
    \item I thought the system was easy to use.
    \item I think that I would need the support of a technical person to be able to use this system.
    \item I found the various functions in this system were well integrated.
    \item I thought there was too much inconsistency in this system.
    \item I would imagine that most people would learn to use this system very quickly.
    \item I found the system very cumbersome to use.
    \item I felt very confident using the system.
    \item I needed to learn a lot of things before I could get going with this system.
\end{enumerate}


\begin{enumerate}\label{FinalTestQuestions}
    \item What did you just experience?
    \item What did you notice about the radio?
    \item What did you notice about the environment?
    \item Did you feel like eating less burgers during the course of the game? -if yes, why?
    \item Why do you think the environment changed?
    \item What do you think the message of the game was?
    \item What do you think the burger meant?
    \item What do you think the purpose of the radio was?
    \item Did you feel that the message came on too strong?
    \item Would you consider eating less meat, after this experience?
    \item Did you feel like you got a new perspective on meat consumption? -if yes, how did it change?
\end{enumerate}