\chapter{Design}
This section will present the process of creating the design of the prototype that will attempt to change the behaviour of the user. The design is based on theory gathered in the analysis chapter. 

\section{Initial Design Ideas}
After establishing the design requirements, different concept ideas based on said requirements were thought up. All these concept ideas were based on the idea of changing the behaviour towards climate action using research gathered from the analysis formed into an artefact. Initial design ideas were brainstormed based on the requirements to come up with some different designs. Below is all the different concepts thought up, these were then combined and mixed a bit into a final concept.

Initial idea / vision - House

\begin{itemize}
    \item Get to work Sim
    \begin{itemize}
        \item Fun mini games
        \item Choice driven narrative
    \end{itemize}
    \item House
    \begin{itemize}
        \item Based on the Hollywood model
        \item STEVE
        \item Interactive Narrative
        \item Novelty interactions
        \item Exaggerated feedback
    \end{itemize}
    \item Local God Sim
    \begin{itemize}
        \item Overview effect
        \item Exaggerated feedback
        \item Very in your face
    \end{itemize}
    \item 60 seconds climate saver
    \begin{itemize}
        \item Very embedded since climate change is not the focus
        \item Interesting mechanics, strong engagement
    \end{itemize}
    \item Space Mars Thing
    \item Narrative Driver
    \begin{itemize}
        \item Similar to house
        \item Narrative based concept
        \item Novelty interactions
        \item Exaggerated feedback
    \end{itemize}
    \item Narrative Astronaut
\end{itemize}

\section{Final Concept - Initial Design}
Narrative Driver, a game where you sit in a car and listen to a story about the environment. The purpose of the final concept is to incite a behaviour change in the user in regards to Co$_2$ emissions. To do this, it was important to incorporate the design requirements, that first of provided the user with an understanding of the problem, but also make them immersed and engaged in the activities tackling the problem. Based on the research it was decided that the concept should be an immersive, narrative driven story, and use exaggerated feedback to incite this behaviour change.

Narrative Driver, is a virtual environment where the user will be placed in a car, and the goal is to drive the car whilst listening to a story regarding Co$_2$ emissions. The player will be presented with choices along the road they are driving on. The environment will then change depending on these choices, and the user will be able to observe how their choices affect the world around them. 

The game-play mechanics is not the focus of this game, and it is using novelty interactions to give the user an opportunity to partake in the virtual world, while still being heavily driven by the story.